---
title: "Kinase search"
author: "Alix Harlington"
date: "03/02/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(pander)
library(readr)
library(ampir)
```

## Download the .csv protein files of organism/s of interest into the same working directory as this .Rmd.

## Make a list of dataframes based on the .csv files in the directory. Combine them into a single dataframe and rename some column names.

```{r rawdata}
rawdata <- list.files(path = "~/Bacteria filter list/1_P450_search/", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows() %>%
  rename(
    Locus_tag = `Locus tag`,
    Protein_ID = `Protein product`,
    Protein_name = `Protein Name`,
    Species = Accession
  ) %>%
  select(Species, Start, Stop, Strand, GeneID, Locus, Locus_tag, Protein_ID, Length, Protein_name)
rawdata

```

## Filter this dataframe for P450 proteins and arrange the protein_product numbers from smallest to largest ID number. (This makes it easier when using batch entrez to ensure lists are in the same order)

```{r filter}
filterdata <- rawdata %>%
  select(-GeneID, -Locus, Locus_tag) %>%
  filter(str_detect(Protein_name, "P450|ferredoxin")) %>%
  arrange(Protein_ID)
filterdata
```

```{r tally}
tally(filterdata)
```

## Export a .csv file of the protein ID for use and upload to batch Entrez.
### Once this file is made upload it to the batch entrez website and download the fasta file containing the amino acids sequences.

```{r proteinlist}
proteinlist <- filterdata %>%
  select(Protein_ID) %>%
  arrange(Protein_ID)
proteinlist

write_csv(proteinlist, file = "~/Bacteria filter list/1_P450_search/Proteins_P450/ferredoxin_P450.csv")
```

## Once you download the fasta file from batch entrez the command read_faa will take a fasta file and convert it to a dataframe.
## Seperate is used to remove species and protein name from the first column and rename it to protein_product.

```{r}
fastafile <- read_faa(file = "~/Bacteria filter list/1_P450_search/ferredoxin_P450_proteins.fasta") %>% separate(seq_name, into = c("Protein_ID"), sep = " ")

fastafile

write_csv(fastafile, file = "~/Bacteria filter list/1_P450_search/Proteins_P450/ferredoxin_P450_fasta.csv")
```

## Export the final results containg the species ID, start, stop, strand, protein ID, Length, protein name and sequence.

```{r}
finaldata <- inner_join(filterdata, fastafile) %>%
  select(-Locus_tag)
finaldata

write_csv(finaldata, file = "~/Bacteria filter list/1_P450_search/Proteins_P450/ferredoxin_P450_final.csv")
```

